### 2021-05-14 compound_examples.tex
First draft (s.t. examples)

Here we will study the optimal designs in terms of the criteria (\ref{eq::MSE_D}), (\ref{eq::MSE_D_point}) and (\ref{eq::MSE_L}) (referred to as $MSE(D)$, $MSE(D)P$ and $MSE(L)$ criteria respectively) in the framework a factorial experiment, with $5$ factors, each is at three levels. The small number of runs ($40$) allows estimation of the full-second order polynomial model ($p=21$), but we assume that the `true' model contains also all third-order terms (linear-by-linear-by-linear and quadratic-by-linear interactions), $q=30$ of them in total.. 
[Some comparison with other criteria is to be added]

>>>>

[OE: To be edited]

Here we will study the optimal designs in terms of the criteria (\ref{eq::MSE_D}) and (\ref{eq::MSE_L}) (referred to as $MSE(D)$, $MSE(D)P$ and $MSE(L)$ criteria respectively) in the framework a factorial experiment, with $5$ factors, each is at three levels. The small number of runs ($40$) allows estimation of the full-second order polynomial model ($p=21$), but we assume that the `true' model contains also all third-order terms (linear-by-linear-by-linear and quadratic-by-linear interactions), $q=30$ of them in total.. 
[Some comparison with other criteria is to be added]
